UCD\\MSc Thesis Proposal:\\\emph{An approach for Continuous Capacity Planning in Cloud Environments with Uptime-based Pricing Model}

### 2015-04-16 paper/paper.tex
changes

\ForAll{machine in otherMachines}{
        \If{$machine.cpu < cluster.cpu$} {
                 $spareCpu += clusterCpu - machineCpu$
        }
        \If{$machine.memory < cluster.memory$}{
        	$spareMemory += clusterMemory - machineMemory$
        }
}

@@

\begin{algorithm}[h]
\caption{New configuration suggestion}
\label{alg:new_configuration}
 \KwData{List of machines from Threshold Based Report, List of available schemes;}
 \KwResult{List of machines that can be powered down}
 \algrenewcommand\algorithmicfunction{\textbf{class}}
 \algrenewcommand\algorithmicprocedure{\textbf{method}}

\ForAll{machine in otherMachines}{
        \If{$machine.cpu < cluster.cpu$} {
                 $spareCpu += clusterCpu - machineCpu$
        }
        \If{$machine.memory < cluster.memory$}{
                $spareMemory += clusterMemory - machineMemory$
        }
}

>>>>

\ForAll{machine in otherMachines}{
        \If{$machine.cpu < cluster.cpu$} {
                 $spareCpu += clusterCpu - machineCpu$
        }
        \If{$machine.memory < cluster.memory$} {
        	$spareMemory += clusterMemory - machineMemory$
        }
}

@@

\begin{algorithm}[h]
\caption{New configuration suggestion}
\label{alg:new_configuration}
 \KwData{List of machines from Threshold Based Report, List of available schemes, Average number tasks per hour;}
 \KwResult{New configuration suggestion}
 \algrenewcommand\algorithmicfunction{\textbf{class}}
 \algrenewcommand\algorithmicprocedure{\textbf{method}}

  $float[ ] totalCost;$
  $float totalCpu = 0;$
  $float totalMemory = 0;$

\ForAll{machine in machinesFromReport}{
        machine.cpu += totalCpu
        machine.memory += totalMemory
}

\ForAll{scheme in availableSchemes}{
		hoursPerDay = scheme.getHours()
        \If{$machine.cpu < cluster.cpu$} {
                 $spareCpu += clusterCpu - machineCpu$
        }
        \If{$machine.memory < cluster.memory$} {
                $spareMemory += clusterMemory - machineMemory$
        }
}
